### 2016-11-28 Hhh/Hhh.tex
Fixing up some more of Gavins comments on H->hh chapter

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter THEORY, in some MSSM scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

@@

In signal events, the di--tau pair and di--jet pair 
are the decay products of a 125 GeV Higgs boson, therefore their invariant
masses should be close to 125 GeV. To reduce background contributions
from events where the di--tau or di--jet mass is not compatible with
125 GeV, requirements are made on the di--jet invariant mass and the di--tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $Z\rightarrow\Pgt\Pgt$ and $H\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the SM $H\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150 $GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

@@

As illustrated in figure \ref{fig:kinfitvsmjj} the use of the kinematic fit greatly
improves the resolution of the reconstructed heavy Higgs mass in signal events, when 
compared with the simple 4-body mass reconstruction. It also shifts the mean of the
distribution closer to the true value. From the right hand side of
figure \ref{fig:kinfitvsmjj} we can see that the mass distribution for
background events is affected less by the kinematic fit, although due to the
invariant mass constraint the minimum of the reconstructed mass distribution
is forced to 250 GeV.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data--driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category, the total
yield after the initial event selection (before subdividing into categories) as
estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from \ttbar backgrounds in the embedded
sample is accounted for by subtracting this contamination, as evaluated using
the dedicated \ttbar embedded samples, from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
These are checked against data in dedicated control regions, one such control
region uses the \emu final state of the taus. An \ac{MC}-to-data correction factor is estimated in 
this control region and applied to the yield estimate from \ac{MC} in the signal region. 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than 30 GeV. To estimate the remaining contribution
from \Wjets in the signal region a sideband with \mT~greater
than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to low- \mT~
extrapolation factor is determined from the \Wjets \ac{MC} 
samples. The yield in the signal region is then the other-background-subtracted
data yield in the high-\mT~region multiplied by this extrapolation factor.
In the 2jet-2tag, a slightly different high-\mT~sideband of 60-120 GeV is used 
to give more events for the \Wjets estimate after other backgrounds are
subtracted. The method of extrapolating this yied estimate into
the signal region is otherwise analogous.

The shape of the \Wjets distribution is taken from the \ac{MC} samples. To 
increase the number of events for this estimate, the b-tagging definition
in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
working point for the purposes of shape estimation.
\subsection{QCD}
\label{sec:hhh_backgrounds_qcd}
A fully data-driven method is used to estimate the QCD background. Data events
passing the signal region selection cuts, but with di-\Pgt candidates of
the same sign, are used for this. The contributions from other backgrounds are 
subtracted, and the contribution from opposite- and same-sign QCD are
not exactly the same an OS/SS ratio is applied to the data-other backgrounds in the same--sign region.
The OS/SS ratio is measured using data with the 
the electron/muon isolation requirements inverted.

@@

uncertainties (which affect both the yield and shape of a process). Section \ref{sec:hhh_results_extraction}

@@

The uncertainty on the luminosity measurement amounts to 2.6\% for data collected during

@@

A systematic uncertainty due to the uncertainty in efficiency measurements

@@

the \Pgt legs of the triggers. This uncertainty is applied to all processes for which

@@

$\mu\rightarrow\Pgt$ fake rate measurement is 30\%. The central value of the $\mu\rightarrow\Pgt$

@@

The b-tag scale factors are varied within their uncertainties to determine the effect

@@

leads to a 1-10\% uncertainty, depending on category and process considered.

@@

\item \Ztautau : the normalisation of the embedded samples attracts a 3.3\% uncertainty, which is derived

@@

\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\%
\item \ttbar: the uncertainty on the \ttbar cross section is 10\%
\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\%
\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the statistics available in the control region, the uncertainty ranges from 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry
\item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio. This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category.

@@

The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty. As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.

@@

The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT~and $\eta$ dependent uncertainty. Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty.

@@

In this section a summary of the \AtoZhtolltautau analysis, which is combined with the 

@@

First the \PZ candidate is chosen as a pair of isolated electrons or muons, with opposite charge, and 
invariant mass of the pair between 60-120 GeV. In case there is more than one possible pair, the 
pair with invariant mass closest to the \PZ mass is chosen. The \htotautau decay is chosen by selecting
an oppositely charged pair of isolated leptons in the four channels mentioned earlier. To ensure no overlap
between different final states is possible, events with additional electrons or muons satisfying the
\pT~and $\eta$ requirements are discarded.

@@

For signal extraction, the mass of the A boson \mA is used. This mass is reconstructed by combining the
4-vector of the \PZ candidate with the 4-vector of the \Ph -candidate as obtained by using the 
\texttt{SVFit} algorithm. The expected and observed 95\% confidence level upper limits, for
all $\ell\ell\tau\tau$ final states combined, is shown in figure \ref{fig:AZhUpperLimits}

@@

More detail on this analysis can be found in reference \cite{CMS-HIG-14-034}.
Systematic uncertainties are also applied in the \AtoZhtolltautau analysis. 
For the purposes of combining the results with the \Htohhtobbtautau search,
some of these are correlated between the two analyses.
This applies to the
luminosity uncertainty and the uncertainties on b-tagging efficiency
and light jet mistagging rate.

\section{Results}
\label{sec:hhh_results}
\subsection{Signal extraction}
\label{sec:hhh_results_extraction}
The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable in this analysis.
For each channel and category, the compatibility of the $m_{H}^{\text{kinfit}}$ distribution
of the observed data with the expected background distribution can be assessed. All bins
of the $m_{H}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
methods used for this were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
and are used for all Higgs analyses in ATLAS and CMS.

For the data a likelihood function is constructed as (equation \ref{eqn:hhh_likelihood}).
\begin{equation} \label{eqn:hhh_likelihood}
\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta)
\end{equation}

Where $\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given as (equation \ref{eqn:hhh_poisson}), with $n_i$ the number of 
data events, whether observed or pseudo-data, in bin i.
\begin{equation}\label{eqn:hhh_poisson}
\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))}
\end{equation}

The first term of equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
in all channels and categories. $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The systematic uncertainties discussed in section 
\ref{sec:hhh_uncs} are each represented by a nuisance parameter $\theta_j$. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to 1 pb, so the signal strenght modifier represents
the cross-section $\times$ branching ratio of a possible signal.

The second term of equation \ref{eqn:hhh_likelihood} $p(\tilde{\theta}|\theta)$ represents the full set of 
probability density functions of the uncertainties on the nominal
values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
as discussed in section\ref{sec:hhh_uncs}. The functional form of the probability density function
depends on the type of systematic uncertainy. Normalisation uncertainties are applied as log-normal constraints.
For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
yields do not become negative. Shape uncertainties are accounted for using a vertical template morphing
technique. For each nuisance parameter that affects the shape of the fitted distribution, two additional
templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
parameter $\lambda$ is added to the likelihood model as a gaussian constraint to smoothly interpolate between
the nominal and $\pm 1\sigma$ templates. Limitations in event statistics for shape templates
are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
shape template are allowed to float within their statistical uncertainty, independent of the other bins. These
variations are controlled by log-normal constraints in the likelihood function.

To compare the data with the background only and signal + background hypotheses, a test
statistic $q_{\mu}$ can be defined. This is a single 
number that is used to distinguish between the two hypotheses. The test
statistic used for LHC Higgs analyses, known as the profile likelihood, is given 
in equation \ref{eqn:hhh_profilelikelihood}.
\begin{equation}\label{eqn:hhh_profilelikelihood}
q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}
\end{equation}

@@

The probabilities of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal+background hypothesis
and assuming the background-only hypothesis, are given in equations \ref{eqn:hhh_pvaluesig} and \ref{eqn:hhh_pvaluebkg}, respectively.

\begin{equation}\label{eqn:hhh_pvaluesig}
p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \int_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu}
\end{equation}

\begin{equation}\label{eqn:hhh_pvaluebkg}
1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} 
\end{equation}

Where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability density functions of $q_{\mu}$ under
the signal+background and background-only hypotheses.

Using this, $CL_s$ is defined as (equation \ref{eqn:hhh_cls})
\begin{equation}\label{eqn:hhh_cls}
CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}
\end{equation}

The value of $\mu$ for which $CL_s{\mu}$ equals $\alpha$ is referred to as the upper limit on $\mu$ at
confidence level $1-\alpha$. Upper limits at the LHC are generally
quoted at 95\% confidence level. %, therefore the upper limit on cross-section times branching ratio
%for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
%equals 0.05. The use of $CL_s$ to set
The use of $CL_s$ to set exclusion limits is referred to as the modified frequentist approach\cite{CLS}.

The distributions $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu}|0,\hat{\theta_0})$ are determined
using toy MC datasets. These datasets are generated from the signal+background or background-only expectations respectively. 
For each toy dataset the nuisance parameters are fixed to their best-fit values as found in the fit to observed data.
The rates of each bin in the toy dataset are set using poisson fluctuations around the expectation in that bin, and the effect of
systematic uncertainties is taken into account by sampling a set of pseudo measurements $\tilde{\theta}'$ for each toy, based on the 
pdf $p(\tilde{\theta}|\theta)$.
The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal+background or background-only)
can by found be accumulating a large number of toy datasets and evaluating $q_{\mu}$ for each of them.

This method of generating toy MC datasets is computationally intensive.
In the limit of large statistics $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
This formula, known as the asymptotic approximation, allows for the calculation
of the observed limit as well as the median and $\pm 1$ and $2\sigma$ expected limits using
the properties of the Asimov dataset, a dataset in which the observation in 
each bin exactly matches the predictions of the model. This method is used for the analysis
described in this chapter, removing the need to generate toy datasets.

@@

The $m_{H}^{\text{kinfit}}$ distributions in all categories of the \mutau and \etau channels, after the fit to
observed data has been performed, are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
respectively.

@@

None of these distributions show hints of an excess.

The model-independent 95\% CL expected and observed upper limits are shown in the left-hand side 
panel of figure \ref{fig:hhh_results_modelindep}, with the right-hand side of the same figure
showing the expected sensitivity per channel. These figures include the contribution from the 
\tautau channel not described in this chapter. The expected upper limit
on the \Htohhtobbtautau process is around 0.3 pb, the observed ranges
from 0.2 pb at low mass to 0.4 pb at high mass. We can
see that the \mutau channel is the most sensitive at masses lower than 320 GeV, with 
the \tautau channel being the most sensitive beyond this mass point. The \etau channel is always
less sensitive than the \mutau channel, but at low mass it is still more sensitive than the \tautau 
channel.

@@

The couplings of the Higgs bosons to quarks and leptons, and of heavy Higgs bosons to other
particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.

>>>>

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryAtlas,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter THEORY, in some MSSM scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb~region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

@@

In signal events, the di--tau pair and di--jet pair 
are the decay products of a 125 GeV Higgs boson, therefore their invariant
masses should be close to 125 GeV. To reduce background contributions
from events where the di--tau or di--jet mass is not compatible with
125 GeV, requirements are made on the di--jet invariant mass and the di--tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $Z\rightarrow\Pgt\Pgt$ and $H\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the SM $H\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150$ GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

@@

As illustrated in figure \ref{fig:kinfitvsmjj} the use of the kinematic fit greatly
improves the resolution of the reconstructed heavy Higgs mass in signal events, when 
compared with the simple 4-body mass reconstruction. It also shifts the mean of the
distribution closer to the true value. It is also insightful to make such a comparison
for the \ttbar background, which is the dominant background in the most signal-sensitive categories as 
shown in figure \ref{fig:Hhh_selection_bjets}. This comparison between 4-body mass and
kinematic fit mass for \ttbar events is shown on the right hand side of figure 
\ref{fig:kinfitvsmjj}. From this figure we can see that the mass distribution for
background events is affected less by the kinematic fit, although due to the
invariant mass constraint the minimum of the reconstructed mass distribution
is forced to 250 GeV.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data--driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category, the total
yield after the initial event selection (before subdividing into categories) as
estimated in \Ztautau \ac{MC} samples is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from \ttbar backgrounds in the embedded
sample is accounted for by subtracting this contamination, as evaluated using
the dedicated \ttbar embedded samples, from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
These are checked against data in dedicated control regions, one such control
region uses the \emu final state of the taus. An \ac{MC}-to-data correction factor is estimated in 
this control region and applied to the yield estimate from \ac{MC} in the signal region. 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than 30 GeV. To estimate the remaining contribution
from \Wjets in the signal region a sideband with \mT~greater
than 70 GeV is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to low- \mT~
extrapolation factor is determined from the \Wjets \ac{MC} 
samples. The yield in the signal region is given by the data yield in the high-\mT sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of 60-120 GeV is used 
to give more events for the \Wjets estimate after other backgrounds are
subtracted. The method of extrapolating this yied estimate into
the signal region is otherwise analogous.

The shape of the \Wjets distribution is taken from the \ac{MC} samples. To 
increase the number of events for this estimate, the b-tagging definition
in the 2jet-1tag and 2jet-2tag categories is loosened to the loose (instead of medium)
working point for the purposes of shape estimation.
\subsection{QCD}
\label{sec:hhh_backgrounds_qcd}
A fully data-driven method is used to estimate the QCD background. Data events
passing the signal region selection cuts, but with di-\Pgt candidates of
the same sign, are used for this. The contributions from other backgrounds
in this same--sign region are subtracted from the number of data events obtained.
As the contribution from opposite- and same-sign QCD are
not exactly the same an OS/SS ratio is applied to the same--sign region data with other backgrounds subtracted.
The OS/SS ratio is measured using data with the 
the electron/muon isolation requirements inverted.

@@

uncertainties (which affect both the yield of a process and the shape of its kinematic fit mass distribution). Section \ref{sec:hhh_results_extraction}

@@

The uncertainty on the luminosity measurement amounts to 2.6\% \cite{CMS-PAS-LUM-13-001} for data collected during

@@

A systematic uncertainty due to the uncertainty on the efficiency measurements

@@

the \Pgt legs of the triggers \cite{CMS-HIG-14-034}. The identification, isolation and trigger efficiency measurement uncertainties are applied to all processes for which

@@

$\mu\rightarrow\Pgt$ fake rate measurement is 30\% \cite{SMHtautauCMS}. The central value of the $\mu\rightarrow\Pgt$

@@

The b-tag scale factors are varied within their uncertainties, as described in ref. \cite{cms-btag-paper}, to determine the effect

@@

leads to a 1-10\% uncertainty, depending on category and process considered \cite{CMS-HIG-14-034}.

@@

\item \Ztautau : the normalisation of the embedded samples has a 3.3\% uncertainty \cite{CMS-HIG-14-034}, which is derived

@@

\item \Zellell: As this is a very small background after requiring 2 jets, the uncertainty on this estimate is derived from the statistical uncertainty on the yield estimate, which varies between 20-90\% \cite{CMS-HIG-14-034}.
\item \ttbar: the uncertainty on the \ttbar cross section is 10\% \cite{SMHtautauCMS}.
\item di-boson and single top: the uncertainty on the di-boson and single-top cross section is 15\% \cite{SMHtautauCMS}.
\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the number of events available in the control region, the uncertainty ranges from 10\% in the 2jet-0tag cateogry to 100\% in the 2jet-2tag cateogry \cite{CMS-HIG-14-034}.
\item QCD: The QCD normalisation uncertainty is obtained by adding the statistical uncertainty on the data-subtracted same-sign region in quadrature with the 10\% uncertainty on the OS/SS ratio. This yields a 20\% uncertainty in the 2jet-0tag category, a 40\% uncertainty in the 2jet-1tag category and a 60-100\% uncertainty in the 2jet-2tag category \cite{CMS-HIG-14-034}.

@@

The energy of hadronically decaying taus is varied up and down by its 3\% uncertainty \cite{SMHtautauCMS}. As this directly affects the kinematic fit mass distribution this uncertainty is then applied as a shape uncertainty.

@@

The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT~and $\eta$ dependent uncertainty \cite{cms-jec-2011}. Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty.

@@

In this section a summary of the \AtoZhtolltautau analysis \cite{CMS-HIG-14-034}, which is combined with the 

@@

First the \PZ candidate is chosen as a pair of isolated electrons or muons, with opposite charge, and 
invariant mass of the pair between 60-120 GeV. If there is more than one possible pair, the 
pair with invariant mass closest to the \PZ mass is chosen. The \htotautau decay is chosen by selecting
an oppositely charged pair of isolated particles in the four channels mentioned earlier. To ensure no overlap
between different final states is possible, events with additional electrons or muons satisfying the
\pT~and $\eta$ requirements are discarded.

@@

For signal extraction, the mass of the A boson \mA~is used. This mass is reconstructed by combining the
4-vector of the \PZ candidate with the 4-vector of the \Ph -candidate as obtained by using the 
\texttt{SVFit} algorithm. The expected and observed 95\% confidence level upper limits, for
all $\ell\ell\tau\tau$ final states combined, is shown in figure \ref{fig:AZhUpperLimits}

@@

More detail on this analysis can be found in reference \cite{CMS-HIG-14-034}.
Systematic uncertainties are also applied in the \AtoZhtolltautau analysis. 
For the purposes of combining the results with the \Htohhtobbtautau search,
some of these are correlated between the two analyses.
This applies to the
luminosity uncertainty and the uncertainties on b-tagging efficiency
and light jet mis-tagging rate.

\section{Results}
\label{sec:hhh_results}
\subsection{Signal extraction}
\label{sec:hhh_results_extraction}
The kinematic fit mass $m_{H}^{\text{kinfit}}$ is used as the discriminating variable in this analysis.
For each channel and category, the compatibility of the $m_{H}^{\text{kinfit}}$ distribution
of the observed data with the expected background distribution can be assessed. All bins
of the $m_{H}^{\text{kinfit}}$ distribution are used to perform a shape analysis. The 
statistical methods used were developed by the LHC Higgs Combination Group \cite{LHCHComb2011} 
and are used for all Higgs analyses in ATLAS and CMS.

The likelihood function for data, whether observed or pseudo-data, is constructed as 
\begin{equation} \label{eqn:hhh_likelihood}
\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta),
\end{equation}

where $\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given by
\begin{equation}\label{eqn:hhh_poisson}
\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))},
\end{equation}

with $n_i$ the number of 
data events, whether observed or pseudo-data, in bin i.

The first term in equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{H}^{\text{kinfit}}$ distribution 
in all channels and categories. $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to 1 pb, so the signal strength modifier represents
the cross-section $\times$ branching ratio of a possible signal.

The second term in equation \ref{eqn:hhh_likelihood} $p(\tilde{\theta}|\theta)$ represents the full set of 
probability density functions of the uncertainties on the nominal
values of the nuisance parameters $\tilde{\theta}$. Each nuisance parameter represents a systematic uncertainty
as discussed in section \ref{sec:hhh_uncs}. The functional form of the probability density function
depends on the type of systematic uncertainy. Normalisation uncertainties are applied as log-normal constraints.
For a log-normal constraint an $n~\sigma$ upwards pull on a nuisance parameter $\theta$ measured with a systematic
uncertainty $\kappa$ multiplies the yield of processes affected by this nuisance parameter by $(1+\kappa)^n$, while
an $n~\sigma$ downwards pull multiplies the process yields by $(1+\kappa)^{-n}$, ensuring that process
yields do not become negative. Shape uncertainties are accounted for using a vertical template morphing
technique \cite{temp-morph-2011}. For each nuisance parameter that affects the shape of the fitted distribution, two additional
templates corresponding to the quantity varied by $\pm 1 \sigma$ are generated. A nuisance
parameter $\lambda$ is added to the likelihood model as a gaussian constraint to smoothly interpolate between
the nominal and $\pm 1\sigma$ templates. Limitations in the number of events used to construct the shape templates
are accounted for by the Barlow-Beeston method\cite{BarlowBeeston}, in which each of the bins of each 
shape template is allowed to float within its statistical uncertainty, independent of the other bins. These
variations are controlled by log-normal constraints in the likelihood function.

To compare the data with the background-only and signal-plus-background hypotheses, a test
statistic $q_{\mu}$ can be defined. This is a single 
number that is used to distinguish between the two hypotheses. The test
statistic used for LHC Higgs analyses, known as the profile likelihood, is given 
by
\begin{equation}\label{eqn:hhh_profilelikelihood}
q_{\mu} = -2\text{ln}\frac{\mathcal{L}(data|\mu,\hat{\theta_{\mu}})}{\mathcal{L}(\text{data}|\hat{\mu},\hat{\theta})}.
\end{equation}

@@

The probabilities of finding a value $q_{\mu}$ at least as large as the observed value $q_{\mu}^{\text{obs}}$, assuming the signal+background hypothesis
and assuming the background-only hypothesis, are given by

\begin{equation}\label{eqn:hhh_pvaluesig}
p_{\mu} = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{s+b}) = \int_{q_{\mu}^{\text{obs}}}^{\infty} f(q_{\mu} | \mu,\hat{\theta_{\mu}^{\text{obs}}}) dq_{\mu},
\end{equation}

and 
\begin{equation}\label{eqn:hhh_pvaluebkg}
1-p_b = P(q_{\mu} \geq q_{\mu}^{\text{obs}} | \text{b}) = \int_{q_{0}^{\text{obs}}}^{\infty} f(q_{\mu} | 0,\hat{\theta_{0}^{\text{obs}}}) dq_{\mu} ,
\end{equation}

where $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu} | 0,\hat{\theta_0})$ are the probability density functions of $q_{\mu}$ under
the signal+background and background-only hypotheses.

Using this, $CL_s$ is defined as
\begin{equation}\label{eqn:hhh_cls}
CL_s(\mu) = \frac{CL_{s+b}}{CL_b} = \frac{p_{\mu}}{1-p_b}.
\end{equation}

The value of $\mu$ for which $CL_s$ equals $\alpha$ is referred to as the upper limit on $\mu$ at
confidence level $1-\alpha$. Upper limits at the LHC are generally
quoted at 95\% confidence level. %, therefore the upper limit on cross-section times branching ratio
%for the \Htohhtobbtautau process at this level is obtained as the value of $\mu$ for which $CL_s$ 
%equals 0.05. The use of $CL_s$ to set
The use of $CL_s$ to set exclusion limits is referred to as the modified frequentist approach\cite{CLS}.

The distributions $f(q_{\mu}|\mu,\hat{\theta_{\mu}})$ and $f(q_{\mu}|0,\hat{\theta_0})$ are determined
using toy MC datasets. These datasets are generated from the signal-plus-background or background-only expectations respectively. 
For each toy dataset the nuisance parameters are fixed to their best-fit values as found in the fit to observed data.
The number of events in each bin in the toy dataset are set using poisson fluctuations around the expectation in that bin, and the effect of
systematic uncertainties is taken into account by sampling a set of pseudo measurements $\tilde{\theta}'$ for each toy, based on the 
pdf $p(\tilde{\theta}|\theta)$.
The probability distribution function of $q_{\mu}$ under the relevant hypothesis (signal-plus-background or background-only)
can by found be accumulating a large number of toy datasets and evaluating $q_{\mu}$ for each of them.

This method of generating toy MC datasets is computationally intensive.
In the limit of large statistics $f(q_{\mu})$ follows a known formula \cite{AsymptoticFormula}.
This formula, known as the asymptotic approximation, allows for the calculation
of the observed limit as well as the median and $\pm 1$ and $2\sigma$ expected limits using
the properties of the Asimov dataset; a dataset in which the observation in 
each bin exactly matches the predictions of the model. This method is used for the analysis
described in this chapter, removing the need to generate toy datasets.

@@

The $m_{H}^{\text{kinfit}}$ distributions in all categories of the \mutau and \etau channels, after the fit to the
observed data has been performed, are shown in figures \ref{fig:hhh_results_mhkinfit_mutau} and \ref{fig:hhh_results_mhkinfit_etau} 
respectively.

@@

None of these distributions show hints of an excess. The model-independent 95\% CL expected and observed upper limits
on cross-section times branching ratio are shown in the left-hand side 
panel of figure \ref{fig:hhh_results_modelindep}, with the right-hand side of the same figure
showing the expected limit per channel. These figures include the contribution from the 
\tautau channel not described in this chapter. The expected upper limit
on the \Htohhtobbtautau process is around 0.3 pb, the observed ranges
from 0.2 pb at low mass to 0.4 pb at high mass. We can
see that the \mutau channel is the most sensitive at masses lower than 320 GeV, with 
the \tautau channel being the most sensitive beyond this mass point. The \etau channel is always
less sensitive than the \mutau channel, but at low mass it is still more sensitive than the \tautau 
channel.

@@

The couplings of the Higgs bosons to quarks and leptons, and of the heavy Higgs bosons to other
particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.
